Linked Open Social Data for Scientific Benchmarking (Supporting Information document)

### 2016-07-28 supportingInformation.tex
finished rendering tables

\section{Snapshot references}
\label{sreferences}
\pdfpageheight 10in
All the Facebook snapshots are either the result of individuals who downloaded
their data (and donated to the first author) or data downloaded from groups.
In the first case, it is senseless to present references and the. In the second
case, we present the group name and a link to a post in the group where
data and figures were delivered to the group.

@@

>>>>

\section{Snapshot references}
\label{sreferences}
\pdfpageheight 10in
\input{tables/facebookReferences}

@@

\clearpage
\section{Trivial counts in each snapshot}
\input{tables/basicOverall}

### 2016-07-28 tables/nsnapshots.tex
finished rendering tables

\begin{table*}[h!]
\begin{center}
\caption{Number of snapshots from each provenance. Every snapshot is a \texttt{po:Snapshot}; there are three types of the \texttt{po:AASnapshot} class.}
\begin{tabular}{| l | c |}\hline
\textbf{snapshot provenance} & \textbf{number of snapshots} \\\hline\hline\hline
http://purl.org/socialparticipation/po/Snapshot & 117 \\\hline
\end{tabular}\end{center}
\end{table*}

>>>>

\begin{table*}[h!]
\begin{center}
\caption{Number of snapshots from each provenance.}
\begin{tabular}{| l | c |}\hline
\textbf{social protocol} & \textbf{number of snapshots} \\\hline\hline
Algorithmic Autoregulation & 3 \\\hline
Cidade Democrática & 1 \\\hline
Email & 4 \\\hline
Facebook & 88 \\\hline
IRC & 4 \\\hline
ParticipaBR & 1 \\\hline
Twitter & 16 \\\hline\hline
all & 117 \\\hline
\end{tabular}\end{center}
\end{table*}
